---
title: "Initialization environment"
author: "Liang Tong"
date: today
format: html
editor: visual
---

# Step0

install the package

```{r 1}
install.packages("devtools")
install.packages("roxygen2")
install.packages('available')
library(devtools)
```

check if ready

```{r 2}
has_devel()
```

# Step1

create package 'TLRpackage'

```{r 3}
create("TLRpackage")
```

check if available

```{r 4}
available::available("TLRpackage")
```

add example function (create r script in TLRpackage/R folder)

# Step2

before document the package ,should **open TLRpackage.Rproj!!!!**

install()

```         
library(devtools)
document()
load_all()
#?findruns
build()
# then install the tar.gz file!!!!!!restart R after install
 # in devtolls
 install()
```

**!!!!!!restart R after install**

tips: create R script and : **Code \> Insert Roxygen Skeleton**

# Step3

testing the function

Vignettes

```{r 5}

#usethis::use_testthat(3)# not run because of R markdown
#usethis::use_vignette("TLRpackage")
devtools::build_vignettes()
```

make changes in Rmd and finially **devtools::build_vignettes()**

**then find the html in .doc folder**

# Step4

create some readme files

**should in the package folder**

```{r 6}
usethis::use_readme_md() # no code 
#usethis::use_readme_rmd() # with code
#usethis::use_news_md() #for update
#devtools::build() 
#devtools::install() 
#devtools::check() 
```

**then rebuild the package,install,restart R**

# Step5

build website

or **build the pdf maual!**

```{r 7}
#pkgdown::build_site()# have problem working
devtools::build_manual()
```

# Step6 loading data
