---
title: "TLRpackage"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TLRpackage}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TLRpackage)
library(data.table)
library(ggplot2)
```

# 1. TL_read example

## first data set: IRL

read the data, and show the output is a new class : **HDI**

e.g. for variable **year**, the class is **int** ; for variable **country_code**, the class is **char**

```{r 1}
data <- TL_read("hdro_indicators_irl.csv")

class(data)
class(data$'year')
class(data$'country_code')
```

## second data set: JPN

```{r 1.2}
data2 <- TL_read("hdro_indicators_jpn.csv")

class(data)
class(data$'year')
class(data$'country_code')
```

# 2. TL_print example

## first data set: IRL

show first **2** rows

```{r 2}
TL_print(data)
```

## second data set: JPN

```{r 2.2}
TL_print(data2)
```

# 3. TL_summary example

## first data set: IRL

summary data, below show the variable name, class and some basic stats. calculation for variable **year** and **value**

```{r 3}
TL_summary(data)
```

## second data set: JPN

```{r 3.2}
TL_summary(data2)
```

# 4. TL_plot example

## first data set: IRL

plot function example for one country

```{r 4}
TL_plot(data)
```

## second data set: JPN

```{r 4.2}
TL_plot(data2)
```
